\chapter{Input Parameters}
\label{ch:input}

\newcommand{\param}[5]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it Default}: #3\\{\it When it matters}: #4\\{\it Meaning}: #5}}
\newcommand{\myhrule}{{\setlength{\parindent}{0cm} \hrulefill }}

\newcommand{\true}{{\ttfamily .true.}}
\newcommand{\false}{{\ttfamily .false.}}

In this section we describe all the parameters which can be included in the input namelist. 

\myhrule

\section{Resolution parameters}

For any new set of surface geometries you consider, you should vary the resolution parameters in this section to make sure
they are large enough.  These parameters should be large enough that the code results you care about are unchanged under further
resolution increases.

\myhrule

\param{nu\_plasma}
{integer}
{64}
{Always}
{Number of grid points in poloidal angle used to evaluate the integral \todo{XXX} in the outer-to-plasma surface inductance matrix.
Often 64 is a good value.
It is resonable and common but not mandatory to use the same value for nu\_plasma, \parlink{nu\_middle}, and \parlink{nu\_outer}.}

\myhrule

\param{nu\_middle}
{integer}
{64}
{Always}
{Number of grid points in poloidal angle used to evaluate the integral \todo{XXX} in the outer-to-middle surface inductance matrix.
Often 64 is a good value.
It is resonable and common but not mandatory to use the same value for \parlink{nu\_plasma}, nu\_middle, and \parlink{nu\_outer}.}

\myhrule

\param{nu\_outer}
{integer}
{64}
{Always}
{Number of grid points in poloidal angle used to evaluate the integral \todo{XXX} in the outer-to-plasma surface and outer-to-middle surface inductance matrices.
Often 64 is a good value.
It is resonable and common but not mandatory to use the same value for \parlink{nu\_plasma}, \parlink{nu\_middle}, and nu\_outer.}

\myhrule

\param{nv\_plasma}
{integer}
{64}
{Always}
{Number of grid points in poloidal angle used to evaluate the integral \todo{XXX} in the outer-to-plasma surface inductance matrix.
A value of 64 is often good when the number of field periods is more than 1. A higher value like 256 may be needed when the number of field periods is 1.
It is resonable and common but not mandatory to use the same value for nv\_plasma, \parlink{nv\_middle}, and \parlink{nv\_outer}.}

\myhrule

\param{nv\_middle}
{integer}
{64}
{Always}
{Number of grid points in poloidal angle used to evaluate the integral \todo{XXX} in the outer-to-middle surface inductance matrix.
A value of 64 is often good when the number of field periods is more than 1. A higher value like 256 may be needed when the number of field periods is 1.
It is resonable and common but not mandatory to use the same value for \parlink{nv\_plasma}, nv\_middle, and \parlink{nv\_outer}.}

\myhrule

\param{nv\_outer}
{integer}
{64}
{Always}
{Number of grid points in poloidal angle used to evaluate the integral \todo{XXX} in the outer-to-plasma surface and outer-to-middle surface inductance matrices.
A value of 64 is often good when the number of field periods is more than 1. A higher value like 256 may be needed when the number of field periods is 1.
It is resonable and common but not mandatory to use the same value for \parlink{nv\_plasma}, \parlink{nv\_middle}, and nv\_outer.}

\section{Geometry parameters for the plasma surface}

\param{geometry\_option\_plasma}
{integer}
{0}
{Always}
{This option controls which type of geometry is used for the plasma surface.\\

{\ttfamily geometry\_option\_plasma} = 0: The plasma surface will be a plain circular torus. The major radius will be \parlink{R0\_plasma}.
     The minor radius will be \parlink{a\_plasma}.\\

{\ttfamily geometry\_option\_plasma} = 1: Identical to option 0. (This option exists just for consistency with \parlink{geometry\_option\_middle} and \parlink{geometry\_option\_outer}.)\\

{\ttfamily geometry\_option\_plasma} = 2: The plasma surface will be the last surface in the \vmec~file specified by \parlink{woutFilename}.
}

\myhrule

\param{R0\_plasma}
{real}
{10.0}
{Only when \parlink{geometry\_option\_plasma} is 0 or 1.}
{Major radius of the plasma surface, when this surface is a plain circular torus.}

\myhrule

\param{a\_plasma}
{real}
{1.0}
{Only when \parlink{geometry\_option\_plasma} is 0 or 1.}
{Minor radius of the plasma surface, when this surface is a plain circular torus.}

\myhrule

\param{nfp\_imposed}
{integer}
{1}
{Only when \parlink{geometry\_option\_plasma} is 0 or 1.}
{When the plasma surface is a plain circular torus, only toroidal mode numbers that are a multiple of this parameter will be considered.
This parameter thus plays a role like \vmec's {\ttfamily nfp} (number of field periods),
and is used when {\ttfamily nfp} is not already loaded from a \vmec~file.}

\section{Geometry parameters for the middle surface}

\param{geometry\_option\_middle}
{integer}
{0}
{Always}
{This option controls which type of geometry is used for the middle surface.\\

{\ttfamily geometry\_option\_middle} = 0: The middle surface will be a plain circular torus. The major radius will be the 
same as the plasma surface: either \parlink{R0\_plasma} if \parlink{geometry\_option\_plasma} is 0 or 1, or {\ttfamily Rmajor\_p} from the \vmec~{\ttfamily wout} file
if  \parlink{geometry\_option\_plasma} is 2.
     The minor radius will be \parlink{a\_middle}.\\

{\ttfamily geometry\_option\_middle} = 1: Identical to option 0, except the major radius of the middle surface will be set by \parlink{R0\_middle}.\\

{\ttfamily geometry\_option\_middle} = 2: The middle surface will computing by expanding the plasma surface uniformly by a distance \parlink{separation\_middle}.
}

\myhrule

\param{R0\_middle}
{real}
{10.0}
{Only when \parlink{geometry\_option\_middle} is 1.}
{Major radius of the middle surface, when this surface is a plain circular torus.}

\myhrule

\param{a\_middle}
{real}
{1.0}
{Only when \parlink{geometry\_option\_middle} is 0 or 1.}
{Minor radius of the middle surface, when this surface is a plain circular torus.}



\section{Geometry parameters for the outer surface}

\param{geometry\_option\_outer}
{integer}
{0}
{Always}
{This option controls which type of geometry is used for the outer surface.\\

{\ttfamily geometry\_option\_outer} = 0: The outer surface will be a plain circular torus. The major radius will be \parlink{R0\_outer}.
     The minor radius will be \parlink{a\_outer}.\\

{\ttfamily geometry\_option\_outer} = 1: Identical to option 0.\\

{\ttfamily geometry\_option\_outer} = 2: The outer surface will be the last surface in the \vmec~file specified by \parlink{woutFilename}.
}

\myhrule

\param{R0\_outer}
{real}
{10.0}
{Only when \parlink{geometry\_option\_outer} is 1.}
{Major radius of the outer surface, when this surface is a plain circular torus.}

\myhrule

\param{a\_outer}
{real}
{1.0}
{Only when \parlink{geometry\_option\_outer} is 0 or 1.}
{Minor radius of the outer surface, when this surface is a plain circular torus.}

\section{Other parameters}

\myhrule

\param{basis\_set\_option}
{integer}
{1}
{Always}
{Determines which set of basis functions is used.\\

{\ttfamily basis\_set\_option} = 1: Use $\sin(2 \pi [mu+nv])$ basis functions.\\

{\ttfamily basis\_set\_option} = 2: Use $\cos(2 \pi [mu+nv])$ basis functions.\\

{\ttfamily basis\_set\_option} = 3: Use both $\sin(2 \pi [mu+nv])$ and $\cos(2 \pi [mu+nv])$ basis functions.
}

\myhrule

\param{save\_level}
{integer}
{1}
{Always}
{Option related determining how many variables are saved in the \netCDF~output file.  The larger the value, the smaller the output file.\\

{\ttfamily save\_level} = 0: Save everything.\\

{\ttfamily save\_level} = 1: Save everything except the inductance matrices.
}

